---
title: "Assignment B-1: Making a function"
author: "April Hwang"
output: 
    github_document:
    df_print: paged
    theme: cosmo
    highlight: tango
---

# Setup

```{r}
#hide package start up message
suppressPackageStartupMessages(library(tidyverse)) 
suppressPackageStartupMessages(library(testthat)) 

#load libraries
library(tidyverse)
library(datateachr) 
library(testthat)
```

<br>

# Make a Function

As per the requirements for **exercise 2**, this section has been documented using roxygen2 tags. It contains a section title and a function description. The argument has been documented with `@param` and `@return` tags. `@param` has been named as below as to provide information regarding the allowed inputs (including the format necessary with $ sign) as well as a concise description of what the parameter does.

```{r}
#' @title max_minus_min
#' 
#' @description
#' Subtract min value from max value. Remove NA.
#' 
#' @param x Input dataset$column name. Used to take num values from column
#' @return A number
#' 
max_minus_min <- function(x, na.rm = TRUE) {
  max(x, na.rm = na.rm) - min(x, na.rm = na.rm)
}
```

<br>

# Examples

**Example 1**: For this example, I will calculate the difference between max and min for `original_price`. 

I will familiarize myself with the dataset by glancing at `original_price`. I will start by sorting the column from highest to lowest. From this, I can see that the two highest games cost $730,640 and $650,560. They are likely outliers and will be removed.

```{r}
#original_price highest to lowest
steam_games %>%
  select(name, original_price) %>%
  arrange(desc(original_price))
```

<br>

I will now sort `original_price` from lowest to highest. From this, I can see that many games are actually free. For the purpose of demonstrating the `max_minus_min()` function, I will remove the free games.

```{r}
#original_price lowest to highest
steam_games %>%
  select(name, original_price) %>%
  arrange(original_price)
```

<br>

The `max_minus_min()` function shows that the difference between the maximum original price (999.00) and minimum original price (0.5) is 998.5.

```{r}
#eliminate two highest priced games and the free games
updated_sg <- steam_games %>%
  select(name, original_price) %>%
  arrange(desc(original_price)) %>%
  filter(!row_number() %in% c(1, 2)) %>%
  filter(original_price != 0)

#calculate max minus min for original price
max_minus_min(updated_sg$original_price)
``` 

<br>

**Example 2**: For this example, I will group by `type` (app, bundle and sub; remove NA) and calculate the difference between max and min of `original_price` of each group. 

```{r}
#group by types and calculate max minus min for each group
grouped_sg <- steam_games %>%
  arrange(desc(original_price)) %>%
  filter(!row_number() %in% c(1, 2)) %>%
  filter(original_price != 0) %>%
  filter(!is.na(types)) %>%
  group_by(types) %>%
  summarise(price_diff = max_minus_min(original_price))

print(grouped_sg)
```

<br>

**Example 3**: I will calculate the max minus min difference in the achievement number. I will familiarize myself with the dataset by examining the column,  `achievements`. From this, I can see that the highest achievement number is 9821.

```{r}
#achievements highest to lowest
steam_games %>%
  select(name, achievements) %>%
  arrange(desc(achievements))
```

<br>

I will now sort `achievements` from lowest to highest. From this, I can see that the lowest achievement number is 1.

```{r}
#achievements lowest to highest
steam_games %>%
  select(name, achievements) %>%
  arrange(achievements)
```

<br>

Based on the above information, I will not remove any outliers and run the function with the dataset as is. The `max_minus_min()` function shows that the difference between the maximum achievement number (9821) and minimum achievement number (1) is 9820.

```{r}
#calculate max minus min for achievements
max_minus_min(steam_games$achievements)
```

<br>

# Test the Function

I will test that the `max_minus_min()` function on `original_price` runs as expected using the `testthat` package.

```{r}
#expect_equal
test_that('Expected value is correct', {
  expect_equal(max_minus_min(updated_sg$original_price), 998.5)
})

#expect_gt and expect_lt
test_that('Output is greater than 0 and less than 1000', {
  expect_gt(max_minus_min(updated_sg$original_price), 0)
  expect_lt(max_minus_min(updated_sg$original_price), 1000)
})

#expect_true and expect_false
test_that('Expected value results in TRUE', {
  expect_true(max_minus_min(updated_sg$original_price) == 998.5)
  expect_false(max_minus_min(updated_sg$original_price) != 998.5)
})
```


